Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis

### 2023-06-28 paper/ATE/cover_letter.tex
ATE update5

\documentclass[a4paper,10pt]{letter}
\usepackage{amsmath}
\usepackage{xcolor}
\linespread{1.2}
\begin{document}
\pagestyle{headings}
\begin{letter}{Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}

\opening{Dear Dr. Christos N. Markides,}

Enclosed you will find an electronic submission of a manuscript entitled ``Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis''. It is an original paper that has already been submitted to the journal Energy and rejected due to insufficient communication of the proposed method in the results section. We updated the manuscript based on the reviewers' comments and suggestions, and hope that we managed to make the manuscript more readable and of higher quality.

@@

Sincerely yours, \\
Lenka Gal\v{c}\'{i}kov\'{a}, Petronela Belkov\'{a}, and Juraj~Oravec
% \closing{Sincerely yours,\\Juraj~Oravec, Michaela Horv\'{a}thov\'{a}, and Monika Bako\v{s}ov\'{a}}

>>>>

\documentclass[a4paper,10pt]{letter}
\usepackage{amsmath}
\usepackage{xcolor}
\linespread{1.2}
\begin{document}
\pagestyle{headings}
\begin{letter}{Professor Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}

\opening{Dear Professor Christos N. Markides,}

Enclosed you will find an electronic submission of a manuscript entitled ``Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis''. It is an original paper that has already been submitted to the journal Energy and rejected due to insufficient communication of the proposed method in the results section. We carefully revisited and updated the manuscript based on the reviewers' comments and suggestions, and hope that we managed to make the manuscript more readable and of higher quality.

@@

Sincerely Yours, \\
Lenka Gal\v{c}\'{i}kov\'{a}, Petronela Belkov\'{a}, and Juraj~Oravec
% \closing{Sincerely yours,\\Juraj~Oravec, Michaela Horv\'{a}thov\'{a}, and Monika Bako\v{s}ov\'{a}}
